PANCHANGE_analysis

### 2020-12-09 PANCHANGE_analysis.Rmd
corrected figure path

opt_chunk$set(fig.path="./figures")

@@

### disorder (no PCL)
```{r forest plot by disorder prepan, fig.height=14, fig.width=8}

@@

>>>>

knitr::opts_chunk$set(fig.path="figures/")

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=14, fig.width=8}

@@

```{r forest plot by disorder retro no pcl, fig.height=14, fig.width=8}
